---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
#install.packages("tidyverse")
#install.packages("palmerpenguins")
#install.packages("babynames")
#install.packages("gh")
#install.packages("here")
#install.packages("httr")
#install.packages("spotifyr")
library(tidyverse)
library(babynames)
library(gh)
library(here)
library(httr)
library(janitor)
library(jsonlite)
library(knitr)
library(lubridate)
library(pdftools)
library(purrr)
library(rvest)
library(spotifyr)
library(tesseract)
library(tidyverse)
library(usethis)
library(xml2)
```


# Introduction
```{r}
NASA_APOD_20190719 <-
  GET("https://api.nasa.gov/planetary/apod?api_key=DEMO_KEY&date=2024-07-19")

# APOD July 19, 2019
content(NASA_APOD_20190719)$date

content(NASA_APOD_20190719)$title

content(NASA_APOD_20190719)$explanation

content(NASA_APOD_20190719)$url
```
# Data {#sec-data}


```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it. 



# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.  

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.


### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results





# Discussion


# References


